---
title: "PEARL+ Weekly Team Review"
subtitle: "Operational Performance & Quality Dashboard"
date: today
format: 
  docx:
    toc: false
    number-sections: false
    highlight-style: github
    reference-doc: landscape_reference.docx
execute: 
  echo: false
  warning: false
  message: false
---

# Setup {visibility="hidden"}

```{r}
#| label: setup

library(here)
library(tidyverse)
library(flextable)
library(qs2)

# Source functions and load latest data bundle
source(here::here("R", "05_output_functions.R"))
load_latest_tidy_data()
```

```{r}
#| label: week-narrative-data

target_week <- max(weekly_data$period_start, na.rm = TRUE)

week_screening <- screening_data %>%
  filter(week_reg == target_week)

eas_registered <- week_screening %>%
  distinct(ea) %>%
  filter(!is.na(ea), ea != "") %>%
  arrange(ea) %>%
  pull(ea)

n_eas <- length(eas_registered)

eas_text <- if (n_eas == 0) {
  "no EAs"
} else if (n_eas == 1) {
  eas_registered
} else if (n_eas == 2) {
  paste(eas_registered, collapse = " and ")
} else {
  paste0(
    paste(eas_registered[-n_eas], collapse = ", "),
    ", and ",
    eas_registered[n_eas]
  )
}

villages_registered <- week_screening %>%
  distinct(village) %>%
  filter(!is.na(village), village != "") %>%
  arrange(village) %>%
  pull(village)

n_villages <- length(villages_registered)

villages_text <- if (n_villages == 0) {
  "no villages"
} else if (n_villages == 1) {
  villages_registered
} else if (n_villages == 2) {
  paste(villages_registered, collapse = " and ")
} else {
  paste0(
    paste(villages_registered[-n_villages], collapse = ", "),
    ", and ",
    villages_registered[n_villages]
  )
}

n_registered <- nrow(week_screening)

n_households <- weekly_data %>%
  filter(period_start == target_week) %>%
  pull(hh_screened)
```

## Summary

This week (`r format(target_week, "%d %b %Y")`), the PEARL+ team registered
participants from `r n_eas` `r if (n_eas == 1) "EA" else "EAs"`
(`r eas_text`) and `r n_villages` `r if (n_villages == 1) "village" else "villages"`
(`r villages_text`). We registered `r n_registered` participants from
`r n_households` unique households.

```{r}
#| label: project-core-table

out_tab_project_weekly_review(core_only = TRUE, table_width = 10)
```

{{< pagebreak >}}

## Weekly Activity

```{r}
#| label: team-core-table
out_tab_team_weekly_review(period = "current", core_only = TRUE) %>%
  flextable::autofit() %>%
  flextable::fit_to_width(10)
```

{{< pagebreak >}}

```{r}
#| label: project-quality-plot
#| fig-width: 9
#| fig-height: 5
#| fig-align: center

out_plot_weekly_quality()
```

{{< pagebreak >}}

## EA Progress

```{r}
#| label: ea-coverage-plot
#| fig-width: 9
#| fig-height: 5
#| fig-align: center

out_plot_ea_coverage()
```

{{< pagebreak >}}

```{r}
#| label: village-cumulative-coverage-plot
#| fig-width: 9
#| fig-height: 5
#| fig-align: center

out_plot_village_cumulative_coverage()
```

{{< pagebreak >}}

## Team Feedback & Action Items

-   **Data Quality:** \[Add manual notes here before the meeting, or discuss live\]
-   **Operational Bottlenecks:** \[E.g., Xpert machine status, vehicle access\]
-   **Focus for Next Week:**
    -   \[E.g., Prioritizing follow-up on expected 3-month reviews\]
