---
title: "PEARL+ Weekly Team Review"
subtitle: "Operational Performance & Quality Dashboard"
date: today
format: 
  docx:
    toc: false
    number-sections: false
    highlight-style: github
    reference-doc: landscape_reference.docx
execute: 
  echo: false
  warning: false
  message: false
---

# Setup {visibility="hidden"}

```{r}
#| label: setup

library(here)
library(tidyverse)
library(flextable)

# Source functions and load latest data bundle
source(here::here("R", "05_output_functions.R"))
load_latest_tidy_data()
```

## Project Overview: Core Indicators (Last 12 Weeks)

```{r}
#| label: project-core-table

out_tab_project_weekly_review(core_only = TRUE)
```

{{< pagebreak >}}

## Project Overview: Weekly Quality Trends

```{r}
#| label: project-quality-plot
#| fig-width: 9
#| fig-height: 6
#| fig-align: center

out_plot_weekly_quality()
```

{{< pagebreak >}}

## Team Performance: Core Indicators (Current Week)

```{r}
#| label: team-core-table
out_tab_team_weekly_review(period = "current", core_only = TRUE)
```

{{< pagebreak >}}

## Team Feedback & Action Items

-   **Data Quality:** \[Add manual notes here before the meeting, or discuss live\]
-   **Operational Bottlenecks:** \[E.g., Xpert machine status, vehicle access\]
-   **Focus for Next Week:**
    -   \[E.g., Prioritizing follow-up on expected 3-month reviews\]
