---
title: "PEARL+ Leprosy Grant Periodic Report"
subtitle: "Reporting Period: `r params$report_start` to `r params$report_end`"
date: today
format:
  docx:
    toc: false
    number-sections: false
    highlight-style: github
    reference-doc: landscape_reference.docx
execute:
  echo: false
  warning: false
  message: false
params:
  report_start: "2026-01-01"
  report_end: "2026-06-30"
  full_project_interval: "quarter"
---

<!--
Rendering this document (via the Render button or `quarto render`) produces
Quarto/03_LRI_report.docx, next to this .qmd - Quarto has no way to redirect
a standalone document's output to another folder via YAML. The companion
xlsx data package (out_xlsx_lri_report(), in the final chunk below) always
writes to reports/LRI_report/LRI_report_data.xlsx (overwritten each run).
After rendering, manually copy the .docx alongside the .xlsx and datestamp
both filenames for the period you're reporting on, e.g.:
  reports/LRI_report/LRI_report_2026-Q1Q2.docx
  reports/LRI_report/LRI_report_data_2026-Q1Q2.xlsx
-->

# Setup {visibility="hidden"}

```{r}
#| label: setup

library(here)
library(tidyverse)
library(lubridate)
library(flextable)
library(qs)

# Source functions and load latest data bundle
source(here::here("R", "05_output_functions.R"))
load_latest_tidy_data()

report_start <- ymd(params$report_start)
report_end <- ymd(params$report_end)
```

```{r}
#| label: period-narrative-data

period_screening <- screening_data %>%
  filter(en_date_visit >= report_start, en_date_visit <= report_end)

villages_screened <- period_screening %>%
  distinct(village) %>%
  filter(!is.na(village), village != "") %>%
  arrange(village) %>%
  pull(village)

n_villages <- length(villages_screened)

villages_text <- if (n_villages == 0) {
  "no villages"
} else if (n_villages == 1) {
  villages_screened
} else if (n_villages == 2) {
  paste(villages_screened, collapse = " and ")
} else {
  paste0(
    paste(villages_screened[-n_villages], collapse = ", "),
    ", and ",
    villages_screened[n_villages]
  )
}

n_registered <- nrow(period_screening)

n_tb_referred <- sum(period_screening$tb_decision == "Presumptive TB", na.rm = TRUE)
n_tb_confirmed <- sum(period_screening$ntp_diagnosis == "Confirmed", na.rm = TRUE)

n_tst_positive <- sum(period_screening$tst_read_positive == "Positive TST", na.rm = TRUE)
n_tpt_started <- sum(period_screening$calc_any_treatment == "TPT", na.rm = TRUE)

n_scabies <- sum(period_screening$lep_scabies == TRUE, na.rm = TRUE)

n_hbv_referred <- sum(period_screening$prerx_hbv_1 == "Positive", na.rm = TRUE)

n_lep_referred <- sum(period_screening$referred_nlp == TRUE, na.rm = TRUE)
n_lep_confirmed <- sum(period_screening$nlp_diagnosis == "Confirmed", na.rm = TRUE)
```

## Reporting Period Summary

During the reporting period (`r format(report_start, "%d %b %Y")` to
`r format(report_end, "%d %b %Y")`), the PEARL+ team registered
`r n_registered` participants and conducted screening in
`r n_villages` `r if (n_villages == 1) "village" else "villages"`:
`r villages_text`. Of those screened, `r n_lep_referred` were referred for
further leprosy assessment, of whom `r n_lep_confirmed` were confirmed cases.

The PEARL+ programme integrates leprosy screening with TB, TST, scabies, and
Hepatitis B activities. In this same period, `r n_tb_referred` participants
were referred for further TB assessment (`r n_tb_confirmed` confirmed),
`r n_tst_positive` had a positive TST result (`r n_tpt_started` started TB
preventive therapy), `r n_scabies` were identified with scabies, and
`r n_hbv_referred` were referred for Hepatitis B follow-up.

{{< pagebreak >}}

## Leprosy Program Indicators (Full Project History)

```{r}
#| label: lep-indicators-table

out_tab_lep_ind_time(interval = params$full_project_interval, font_size = 7, table_width = 9.5)
```

{{< pagebreak >}}

## Treatment Proportions (Full Project History)

```{r}
#| label: treatment-proportions-plot
#| fig-width: 9.5
#| fig-height: 5.5
#| fig-align: center

out_plot_treatment_proportions_time(interval = params$full_project_interval)
```

{{< pagebreak >}}

```{r}
#| label: treatment-proportions-table

out_tab_treatment_proportions_time(interval = params$full_project_interval)
```

```{r}
#| label: xlsx-export

out_xlsx_lri_report(interval = params$full_project_interval)
```
